---
name: Nathalie
surname: Germain
#address:
qualifications: BA
phone: +1 514 716 XXXX
www: github.com/LMD-nat
email: "nathalie.germain.5@ulaval.ca"
#twitter: 
#github: LMD-nat
headcolor: 1b1b1b
# profilepic: nathalie_invite.jpg
# linkedin: nathalie-germain
# bibliography: ""
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tinytex)
install.packages('vitae')
```

# Summary

 * Master of Science student in epidemiology at Université Laval in Québec-City, Canada.
 * Bilingual in English (*native*) and French (*fluent*).
 * I am currently researching the role that caregivers play in reducing early re-admissions to the hospital among elderly patients in Québec.

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where, 
  "Master of Science student, Epidemiology with thesis", "2021-2023", "Université Laval", "Québec, Canada", 
  "Bachelor of Arts in Psychology, honours programme. Graduation with distinction, Arts and Science Dean's List (2016-2017, 2018-2019)", "2016-2019", "Concordia University", "Montréal, Canada",
) %>% 
  detailed_entries(Degree, Year, Institution, Where,)
```

# Awards and honours

```{r}
tribble( ~ Org, ~ Title, ~ Desc, ~ Year,
"Université Laval", "Bourse de recrutement Joseph-Demers", "academic excellence and for study protocol proposed for master's thesis work ($7,500 Award)", "2021",         
"Canadian Psychological Association", "Certificate of Academic Excellence", "having presented one of the best theses at the baccalaureate level at Concordia University", "2019",
"Concordia University", "Garnet Key Society Merit Award", "an outstanding contribution to the 60th Garnet Key Society", "2018",
"Concordia University", "Shuffle Entrance Scholarship", "outstanding academic achievement ($1,000 Award)", "2016") %>% 
  detailed_entries(
    with=Title, 
    what=glue::glue("Awarded for: {Desc}."), 
    where=Org, 
    when=Year
    )
```

# Peer reviewed publications
\setlength{\parindent}{-0.2in}
\setlength{\leftskip}{0.2in}
\setlength{\parskip}{8pt}
\noindent

Devine, S., **Germain, N.**, Ehrlich, S., & Eppinger, B. (2022). Changes in The Prevalence Of Thin Bodies 
Biases Young Womens’ Judgements about Body Size. *Psychological Science* (In press). Project pre-registration : https://osf.io/e28nd

**Germain, N.**, Gonzalez-Barrero, A. M., & Byers-Heinlein, K. (2021). Gesture Development in Infancy: Effects of Gender but not Bilingualism. *Infancy* (In press). Project pre-registration : https://osf.io/gh5q8/

# Presentations
\setlength{\parindent}{-0.2in}
\setlength{\leftskip}{0.2in}
\setlength{\parskip}{8pt}
\noindent

\vspace{1pt}
## Invited talks

**Germain, N.**, Profitt, M., & Eppinger, B. (2021, April 23rd). Individual differences in decision making:   effects of Covid-19. **CRDH Cognition BrownBag**, Concordia University, Montréal, QC. 

**Germain, N.**, Poulin-Dubois, D. (2020, February 21st). Gestural communication among monolingual and bilingual infants. **Bilingualism Interest Group**, Concordia University, Montréal, QC.  

\vspace{1pt}
## Selected poster presentations

**Germain, N.**, Archambault, P. M. (2022, March). Fardeau des proches-aidants des personnes aînées en transition de l'hôpital à la communauté : une série chronologique interrompue. Poster accepted to the **Bâtir ensemble le système de santé apprenant du Québec Symposium**. Virtual conference, Longeuil, QC. [Provincial conference]

Devine, S., **Germain, N.**, Ehrlich, S. & Eppinger, B. (2021, June). Changes in the prevalence of thin bodies biases young women's judgements about body size. Poster presented at the **Annual conference of the Canadian Society for Brain, Behaviour and Cognitive Science (CSBBCS)**. Virtual conference, Montréal, QC. [National conference]

**Germain, N.**, Meltzer, A. & Poulin-Dubois, D. (2021, May). Gestural Communication Among Monolingual and Bilingual Infants. Poster presented at the **2021 Association for Pyschological Science Virtual Convention**. Washington, DC. [International conference]

**Germain, N.**, Profitt, M. & Eppinger, B. (2021, March). Individual differences in decision-making: effects of Covid-19. Poster presented at the **Centre for Research in Human Development (CRDH) Annual Conference 2021**. Concordia University. Montréal, QC. [Provincial conference]


**Germain, N.**, Gonzalez-Barrero, A. M., & Byers-Heinlein, K. (2019, March). Do bilingual babies gesture more than monolinguals as they’re learning to speak? Poster presented at the **PsychoShorts Annual Conference**. University of Ottawa. Ottawa, ON. [National conference]

\vspace{1pt}
## Workshops

**Germain, N.**, (July 9th, 2021). JavaScript for Psychology : using JsPsych and Cognition.run to make simple experiments. Concordia University. Montréal, QC. [Virtual workshop]. Workshop material : https://github.com/LMD-nat/tutorial_jsPsych


# Work experience

```{r}
tribble(
  ~ Lab, ~ Role, ~ Desc1, ~ Desc2, ~ When, ~ Where, 
"Lifespan and Decision Making Laboratory", "Research Coordinator, Supervisor: Dr. Ben Eppinger", "Tasked with designing and conducting behavioural studies relating to cognition.", "Performed analyses of collected data and recruitment of participants.", "August 2020 – August 2021", "Concordia University",
"Le laboratoire de recherche sur le développement du langage et de la cognition", "Research Coordinator, Supervisor: Dr. Diane Poulin-Dubois", "Assigned resources and research projects to student volunteers and conducted recruitment.", "Perfoemd financial administration: operating lab payroll, and management of budget and research funds.", "July 2019 – August 2020", "Concordia University",
"Rent-a-Geek Tutoring", "Statistics tutor", "Reviewed concepts in basic and advanced statistics courses at Concordia with students.", "Assisted students in writing, correcting, and excecuting analyses.", "August 2019 – August 2020", "Montréal, Canada"
) %>% 
  detailed_entries(
    with=Lab, 
    what=Role, 
    why=c(Desc1, Desc2),
    when=When, 
    where=Where
    )
```
# Volunteer experience

```{r}
tribble(
  ~ What,~ Role, ~ Desc1, ~ When, 
"Concordia Journal Of Accessible Psychology","Editor, Coordinator of Social and Public Affairs", "Served as an editor: assigned manuscripts to reviewers and monitored the peer-review process to ensure fairness and timeliness. Promoted and performed outreach for the annual student journal of the department of psychology, organized virtual events.", "August 2020 – August 2021",
"Concordia Infant Research Laboratory","Research assistant under Dr Krista Byers-Heinlein", "Performed data entry management and data collection participation with participating children and parents.", "July 2017 – June 2019",
"West Island Art Hive","Facilitator", "Helped coordinate a community non-profit art studio affiliated with Concordia University's Creative Arts Therapies Department.", "October 2016 – June 2018",
) %>% 
  detailed_entries(
    with=What,
    what=Role,
    why=Desc1,
    when=When
    )

```
# Programming experience

```{r}
tribble(
  ~ What, ~ Desc1, ~ Desc2,
  "Programming languages and proficiency", "Statistical analysis: R (advanced), SAS (intermediate), Python (novice)", "Development and markup : Html, CSS & JavaScript (intermediate), Git, TeX & Markdown (novice)"
  ) %>% 
  detailed_entries(
    with=What,
    why=c(Desc1, Desc2)
    )
```
